---
title: "hw5_p8105"
output: github_document
date: "2024-11-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(ggridges)
set.seed(1)
```

## Problem 2

**2A. Design the elements**
```{r elements}

#mu_values = 0:6
#for i in 1:length(mu_mean)
#define the length in the function not in the loop

#n = 30
#SD = 5
#mean = 0:6
#a = rnorm(30, mean = 0, sd = 5)
#include a in the function so it become repeated sampling, the function use t.test directly

ttest = function(n = 30, mean, sd = 5) {
  df1 = tibble(
    x = rnorm(n = n, mean, sd = sd))
  ttest_result = t.test(x ~1, df1)
  broom::tidy(ttest_result)
}

#writing loop
#use tidy as part of the output immediately to create a tibble
mean_0 = vector("list", length = 5000)

for (i in 1:5000) {
  mean_0[[i]] = ttest(mean = 0)
}

#tidy dataframe result
result0 = bind_rows(mean_0) %>% 
  print()
```

**2B. Loop for mean 1-6**
```{r loop 1-6}
#repeat the above for mean = 1-6, use map is easier
#y should not be part of the expand_grid. we shouldn't have 30 rows, we should have 5000 rows of random sampling containing 30 numbers.
mean_res = 
  expand_grid(
    true_mean = c(0, 1, 2, 3, 4, 5, 6),
    iter = 1:5000
  ) %>% 
  mutate(ttest_result = map(true_mean, ~ttest(mean = .x))) %>% 
  unnest(ttest_result) %>% 
  print()
```

**2C. Make plot for effect size**
```{r effect size}
mean_res %>% 
  mutate(
    estimate = as.numeric(estimate)
  ) %>% 
  select(true_mean, iter, estimate, p.value) %>% 
  group_by(true_mean) %>% 
  mutate(reject_null = p.value < 0.05) %>% 
  summarize(power = mean(reject_null)) %>% 
  ggplot(aes(x = true_mean, y = power)) +
  geom_point() +
  geom_smooth(se = FALSE)
```

**Describe the association between effect size and power**

As the hypothesized true population mean increased, so does the difference with the sample mean. As effect size increase, power will also increase as we can detect difference and thus reject the null. 

**2D. Make plot for mu hat true mu**
```{r mu}
#plot 2
plot2 = mean_res %>% 
  group_by(true_mean) %>% 
  summarize(mean(estimate)) %>% 
  rename(mu_hat_2 = `mean(estimate)`) 

ggplot(plot2, aes(x = true_mean, y = mu_hat_2)) +
  geom_point() +
  geom_smooth(se = FALSE)

#plot 3
plot3 = mean_res %>% 
  filter(p.value < 0.05) %>% 
  group_by(true_mean) %>% 
  summarize(mean(estimate)) %>% 
  rename(mu_hat_2f = `mean(estimate)`)

ggplot(plot3, aes(x = true_mean, y = mu_hat_2f)) +
  geom_point() +
  geom_smooth(se = FALSE)

```

**Is the sample average of mu hat across tests for which the null is rejected approximately equal to the true value of mean? why or why not?**
No, as we see the line is not really linear. This is because when the null is rejected, it means mu != mu hat so they should be different.  

## Problem 3

**3A**
```{r homicide}
#export the data
homicide = read.csv("./data/homicide-data.csv")
```

**Describe the raw data** 
The data contains `r nrow(homicide)` observations. The variables are `r names(homicide)`, which includes date of the crime (in YYYYMMDD format), victim's name and demographics, location of homicide, and the outcome of the investigation. 

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r hom test}
homicide_clean = homicide %>% 
  unite(city_state, c(city, state), sep = ", ") %>% 
  group_by(city_state) %>%
  summarize(
    total = n(), 
    unsolved = sum(disposition != "Closed by arrest")) %>% 
  print()
```

Total number of homicides and unsolved homicides across all city states are `r sum(pull(homicide_clean, total))` and `r sum(pull(homicide_clean, unsolved))`, respectively. 

**3B. Prop test for Baltimore** 

```{r homicide_md}
library(broom)

#prop test for baltimore. x = unsolved, n = total homicide, the rest use default setting
homicide_clean %>% 
  filter(city_state == "Baltimore, MD") %>% 
  mutate(
    prop_test_result = map2(unsolved, total, ~ prop.test(x = .x, n = .y))
  ) %>% 
  mutate(
    tidy_result = map(prop_test_result, broom::tidy)
  ) %>% 
  unnest(tidy_result) %>% 
  select(city_state, estimate, conf.low, conf.high) %>% 
  print()
```

**3C. Prop test for all**

```{r homicide5}
homicide_plot = homicide_clean %>% 
  mutate(
    prop_test_result = map2(unsolved, total, ~ prop.test(x = .x, n = .y))
  ) %>% 
  mutate(
    tidy_result = map(prop_test_result, broom::tidy)
  ) %>% 
  unnest(tidy_result) %>% 
  print()

```

**3D. Homicide plotting** 

```{r plot homicide}
homicide_plot %>% 
  select(city_state, estimate, conf.low, conf.high) %>% 
  arrange(desc(estimate)) %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust  =1))
```



